%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Domain Architect for Shared Platforms \& DevOps} % Job title
{BEC} % Organization
{Roskilde, Denmark} % Location
{Mar. 2021 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Provided architectural guidelines for BEC's shared development platforms.}
\item{Maintained an overall long-term strategic state and a short-term tactical path for the domain.}
\item{Enabled, supported and enhanced DevOps practices by having an architectural overview of the processes, tools and people aspects of developing software in BEC.}
\item{Developed a strategy for monitoring and alerting across services and platforms, and facilitated/lead the implementation from an architectural viewpoint.}
\item{Steering committee member representing architecture in the domain's prioritization.}
\end{cvitems}
}
\cventry
{DevOps engineer} % Job title
{BEC} % Organization
{Roskilde, Denmark} % Location
{Aug. 2018 - Mar. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Embraced a fast-feedback mindset and frequently interacted with customers and stakeholders during development.}
\item Architected and implemented BEC's observability platform based on the ELK stack (Elasticsearch, Logstash, Kibana).
\item Developed automated pipelines in Jenkins for building, testing, releasing and deploying applications.
% \item Set up clusterwide logging on BEC's Openshift (kubernetes) Platform and monitoring of critical applications.
\item Tech lead on teams and promoted the DevOps culture in BEC through workshops, talks and presentations.
\item Enhanced BEC's ability to deliver by establishing good practices for infrastructure-as-code where possible.
\end{cvitems}
}
\cventry
{Software developer} % Job title
{Edlund A/S} % Organization
{Copenhagen, Denmark} % Location
{Sep. 2014 - Jul. 2018 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Working in an Agile and SCRUM inspired environment as an IT-consultant for Life and Pension companies.}
\item {A part of the process from specification to analysis, implementation and pre-testing.}
\item {Developed using .NET and SQL from GUI level to business logic layer and database structure.}
\item {Migration of two sizeable customer populations into Sampensions existing solution.}
\item {Main developer of the implementation of GDPR at Sampension.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{PhD in Mathematical modelling} % Degree
{Danish Technical University and Massachusetts Institute of Technology (MIT)} % Institution
{Kgs. Lyngby, Denmark \newline Boston, Massachusetts, USA} % Location
{Jan. 2011 - Apr. 2014} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Research focused on the mathematical modeling of fluid dynamics, specifically droplets on different surfaces; setting up computational FEM models, examining parameter dependency in Matlab, setting up and performing experiments to compare with numerical results.}
\item Visiting researcher at Massachusetts Institute of Technology (MIT) mathematics department, Sep. 2011 - Mar. 2012. Two papers published on the basis of my visit.
\item Three peer-reviewed published papers on the basis of my thesis, two as first author.
\end{cvitems}
}
\end{cventries}
