%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Skills}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cvskills}

\cvskill
{Languages} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Experienced in Python, C\#, Java. Some experience with groovy}
\end{cvitems}
}

\cvskill
{DevOps} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Managing ELK stack (with elasticsearch as a service).}
\item {Setting up dashboards, monitoring and alerting.}
\item {Doing infrastructure as code, primarily through Jenkins.}
\item {Helm charts and Kubernetes objects-as-code}
\end{cvitems}
}

\cvskill
{CI/CD} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Experienced with developing and maintaining Jenkins as a CI/CD platform.}
\item {Advanced Git and Mercurial knowledge.}
\end{cvitems}
}

\cvskill
{Project methods \& tools} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Experienced in the ways of Scrum and SAFe.}
\item Expert user of JIRA and Confluence
\end{cvitems}
}
\cvskill
{Mathematical modeling} % Category
{
\begin{cvitems}
  \vspace{2mm}
\item {Creating mathematical descriptions of reality}
\item Parameter estimation, parameter grid search
\item ODE solving
\end{cvitems}
}

\cvskill
{Personal} % Category
{
\begin{cvitems}
\item {Outgoing but also self-motivated. I really enjoy working in a team but I also take pride in my own responsibilities.}
\item {Good social skills. If you ask my current colleagues, they would say I am a very well-liked person.}
\item {Curious and interested. I am not afraid to ask questions when there is something I do not understand.}
\item {Logical thinking. I argument and understand through logical reasoning.}
\item {Clear communicator. I am seldom misunderstood and often notice when others are.}
\item {Problem oriented. I think about solutions with the problem as starting point without being limited by subject.}
\item {Quick learner. I pick up new methods or ideas to solve new problems quickly.}
\end{cvitems}} % Skills
 % Skills

% \cvskill
% {Communication} % Category
% {
% \begin{cvitems}
%   \vspace{2mm}
% \item {}
% \end{cvitems}
% } % Skills


%------------------------------------------------

\end{cvskills}
