%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education \& Courses}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{AZ-303: Microsoft Azure Architect Technologies}
{Tekonologisk Institut}
{Copenhagen}
{spring 2021}
{\begin{cvitems}
\item This course teaches Solutions Architects how to translate business requirements into secure, scalable, and reliable solutions. Lessons include virtualization, automation, networking, storage, identity, security, data platform, and application infrastructure. This course outlines how decisions in each theses area affects an overall solution.
\end{cvitems}}

\cventry
{Single subject: Enterprise Architecture}
{ITU}
{Copenhagen}
{Autumn 2020}
{\begin{cvitems}
\item An introduction to key Enterprise Architecture frameworks and concepts, e.g. EA3, Operating Models, Dynamic Enterprise Architecture.
\item Developed an implementation strategy for a strategic initiative in BEC along with an assessment of the architectural maturity within BEC based on the course content.
\end{cvitems}}

\cventry
{Elasticsearch enginer I and II}
{elastic}
{Copenhagen}
{Spring 2019}
{\begin{cvitems}
\item Elasticsearch data modeling; cluster deployment; going from development to production; Elasticsearch nodes and index management.
\end{cvitems}}

\cventry
{Single subject: Advanced Software Engineering}
{ITU}
{Copenhagen}
{Spring 2018}
{\begin{cvitems}
\item Course objective: to enable the participant to analyze, discuss and relate research results to their present work.
\item Themes:
DevOps, Continous Integration, Configuration Management, Application Lifecycle Management, Quality of Software Processes, Distributed Development.
\end{cvitems}}

\cventry
{Other selected courses/conferences} % Degree
{Various locations} % Institution
{} % Location
{2014 - present} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item{DevOps world (conference) - Copenhagen - Fall 2018}
\item{Day of Jenkins as code (conference) - Copenhagen - Fall 2018}
\item {CodeConf (DevOps focused conference) - Copenhagen - Fall 2018 and Fall 2019}
\item {Practical Machine Learning with Functional Programming - NDC London - Spring 2017}
\item {Essential .NET with C\# for .NET 4.5 - London, Developmentor - Fall 2014}
\end{cvitems}
}

\cventry
{MSc in Mathematics and Physics} % Degree
{Roskilde University}
{Roskilde, Denmark} % Location
{Aug. 2003 - Jun. 2010} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Combined degree in Physics and Mathematics.}
\item {Education philosophy emphasizing teaching through problem oriented projects.}
\item Masters thesis in mathematical modelling of the human cardiovascular system. Thesis lead to one published peer-reviewed paper.
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
